%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%  \cventry
%     {API Developer} % Job title
%     {NYU IT} % Organization
%     {NY, USA} % Location
%     {May 2021 - Present} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%       \item {Worked on NYU dashboard which aggregated request information of all the users}
%       \item {Modified requests API to append more fields with user information}
%       \end{cvitems}
%     }

  \cventry
    {Graduate Analyst} % Job title
    {Barclays} % Organization
    {Pune, India} % Location
    {Jul 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Redesigned and migrated existing applications in Online Banking from AngularJS to Angular 9, making the user interface very friendly and at par with current design trends}
         \item {Contributed to enabling merchants as a business segment for the Online banking platform thereby developing front-end, back-end and authorisation solutions for it.
         \item Developed and designed features for merchant on-boarding, overview onto the Online Banking channel, with facilities of download and viewing of transactions. This added around 80,000 customers to the channel.}
        \item {Provided a tactical solution for multi business users and implemented new user experience for a Smart Business Dashboard which increased new registrations by 23\%.Engineered a new UI/UX for Smart Business dashboard, with flexibility's for online update of personal data, which was earlier available only offline.  This new dashboard registered more then 3000 customers in the first week itself.}
        \item {Contributed and  developed a centralised platform for the development of Restful APIs. Developed Restful API for business instant lending feature, with the fault rate decreasing by 20\%}
         \item { Developed a central dashboard for managing API,  with auto triggering jobs in common error scenarios in-turn eradicating manual intervention}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Innoplexus Consulting Services} % Organization
    {Pune, India} % Location
    { May 2016 - Jul 2016 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a centralized platform for crawling , extracting and unifying pharmaceutical data.}
        \item {Automated the ETL(Extraction,Transformation and Load)
processes for the pharmaceutical products Oilbird and Touchpoint.}
        \item {Utilizing Machine Learning, engineered an universal crawler that crawled data from various sources and accordingly segmented with an accuracy of over 89\%.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
%   \cventry
%     {Software Developer Intern } % Job title
%     {DSS Group } % Organization
%     {Goa, India} % Location
%     { May 2015 - Jul 2015} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Created a leave portal for online request / cancellation of
% leave by employees, with real time updates using WAMP stack and PostgreSQL}
%         \item{ Incorporated admin acceptance/cancellation of leave.}
%       \end{cvitems}
%     }
%---------------------------------------------------------


\end{cventries}
